LayeredTypes

### 2022-10-24 paper/paper.tex
* First version of prototype compiler (Parser+Interpreter)

\begin{figure}[ht!]
\begin{align*}
	id \in \texttt{Ident}\ 	&::=\ [a...zA...Z]+ \\
	v \in \texttt{Var}\ 	&::=\ id \\
	f \in \texttt{Fun}\ 	&::=\ id_1\ id_2\ \{\ s\ \}\\
	e \in \texttt{Expr}\ 	&::=\ v\ |\ (\ e\ \circledplus\ e\ )\ |\ (e\ \circleddot\ e)\ |\ c \\
	c \in \texttt{Const}\ 	&::=\ \texttt{True}\ |\ \texttt{False}\ |\ \mathbb{Z} \\
	s \in \texttt{Stmt}\ 	&::=\ v\ :=\ e\ |\ f(v)\ |\ \texttt{if}\ v\ \texttt{then}\ s\ \texttt{else}\ s\ |\ \texttt{let}\ v\ :=\ e\ \texttt{in}\ s\ |\ l \\
	l \in \texttt{Layer}\ 	&::=\ id_1::id_2::\texttt{String} \\
	\circledplus\ 		&::=\ \texttt{+}\ |\ \texttt{-} \\
	\circleddot\ 		&::=\ \texttt{!=}\ |\ \texttt{==}\ |\ \texttt{<} \ |\ \texttt{>} \ |\ \texttt{<=} \ |\ \texttt{>=} \\
\end{align*}
\caption{Syntax of the simple functional language}
\label{fig:lang}
\end{figure}

@@

These layers can then be used to refine an identifier. In a very basic and minimal approach these layers can be used to annotate types to variables and identifiers. Additionally, one might add additional layers to a variable to ensure more properties. Each layer will be checked individually and independently. A more detailled approach of the architecture behind our layered approach will be described in section \ref{ssec:architecture}.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cl} 
      \\
      \(\frac
         {x \ : \ \sigma \ \in \ \Gamma}
        {\Gamma \  \vdash \ x \ : \ \sigma} \) 
      &  [\texttt{Var}]  \\
      \\

      \\
      \(\frac
        {\Gamma \  \vdash \ {e}_{0} \ : \ \tau \rightarrow {\tau}' \;\;\;\; \Gamma \  \vdash \  {e}_{1} \ : \ \tau}
        {\Gamma \vdash {e}_{0} \; {e}_{1} \ : \ {\tau}'} \)
      & [\texttt{App}] \\
      \\

      \\
      \(\frac
        {\Gamma , \ x \ : \ \tau \ \vdash \ e \ : \ {\tau}'}
        {\Gamma \ \vdash \ \lambda x \ . \ e \ : \ \tau \rightarrow{\tau}'}\)
      & [\texttt{Abs}] \\
      \\

      \\
      \(\frac
        {\Gamma \ \vdash \ {e}_{0} \ : \ \sigma \;\;\;\; 
         \Gamma, \ x \ : \ \sigma \ \vdash \ {e}_{1} \ : \ \tau}
        {\Gamma \ \vdash \ \texttt{let} \ x \ = \ {e}_{0} \ \texttt{in} \ {e}_{1} \ : \ \tau}\)
      & [\texttt{Let}] \\ 
      \\

      \\
      \(\frac
        {
            \newline
            \Gamma \ \vdash \ e \ : \ {\sigma}' \;\;\;\;
            {\sigma}' \ \sqsubseteq  \ \sigma
        }
        {
            \Gamma \ \vdash \ e \ : \ \sigma
        }\)
      & [\texttt{Inst}] \\
      \\

      \\
      \(
       \frac
       {
        \Gamma \ \vdash \ e \ : \ \sigma \;\;\;\;
        \alpha \ \notin \text{free}(\Gamma)
       }
       {
        \Gamma \ \vdash \ e \ : \ \forall \ \alpha \ . \ \sigma
       }
      \)
      & [\texttt{Gen}] \\
      \\
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{enumerate}
	\item A parser that parses the input program and creates an abstract syntax tree (AST) of the program (\ref{sssec:parser}).
	\item A layered type checker that checks the defined type layers for the tree incrementally (\ref{sssec:layered_type_checker}).
	\item A code generator that generates the corresponding code for the input program (\ref{sssec:code_generator}).
\end{enumerate}

\subsubsection{Parser}
\label{sssec:parser}

\subsubsection{Layered Type Checker}
\label{sssec:layered_type_checker}

\subsubsection{Code Generator}
\label{sssec:code_generator}

>>>>

\begin{figure}[ht!]
\begin{align*}
	id \in \texttt{Ident}\ 	&::=\ [a...zA...Z]+ \\
	v \in \texttt{Var}\ 	&::=\ id \\
	f \in \texttt{Fun}\ 	&::=\ id_1\ id_2\ \{\ s\ \}\\
	e \in \texttt{Expr}\ 	&::=\ v\ |\ c\ |\ (\ e\ \circledplus\ e\ )\ |\ (e\ \circleddot\ e)\ |\ f(e) \\
	c \in \texttt{Const}\ 	&::=\ \texttt{True}\ |\ \texttt{False}\ |\ \mathbb{Z} \\
	s \in \texttt{Stmt}\ 	&::=\ v\ :=\ e\ |\ \texttt{if}\ v\ \texttt{then}\ s\ \texttt{else}\ s\ |\ \texttt{let}\ v\ :=\ e\ \texttt{in}\ s\ |\ l \\
	l \in \texttt{Layer}\ 	&::=\ id_1::id_2::\texttt{String} \\
	\circledplus\ 		&::=\ \texttt{+}\ |\ \texttt{-} \\
	\circleddot\ 		&::=\ \texttt{!=}\ |\ \texttt{==}\ |\ \texttt{<} \ |\ \texttt{>} \ |\ \texttt{<=} \ |\ \texttt{>=} \\
\end{align*}
\caption{Syntax of the simple functional language}
\label{fig:lang}
\end{figure}

@@

These layers can then be used to refine an identifier. In a very basic and minimal approach these layers can be used to annotate types to variables and functions. Additionally, one might add additional layers to a variable to ensure more properties. Each layer will be checked individually and independently. A more detailled approach of the architecture behind our layered approach will be described in section \ref{ssec:architecture}.

@@

@@

\begin{enumerate}
	\item A parser that parses the input program and creates an abstract syntax tree (AST) of the program.
	\item A layered type checker that checks the defined type layers for the tree incrementally.
	\item A code generator that generates the corresponding code for the input program.
\end{enumerate}
